Hydrodynamics of a Semi-Permeable Vesicle Under Flow and Confinement???

### 2020-12-16 vesicle_code/docs/permeableVes/main.tex
converted tikz to pdf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}
Our analysis shows that a semi-permeable vesicle in a quiescent flow
relaxes to a circle at a rate that is proportional to $\beta$, and the
steady state tension is $\Lambda = 2\pi^2/L^2$. Therefore, the times for
the vesicle to deviate from its initial reduced area and to reach its
steady state are proportional to $\beta^{-1}$. This is verified for a
vesicle with initial reduced area $\alpha = 0.65$ and with different
semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
to be within 1.3\% of its steady state reduced area, and the required
time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
1.3\% of its initial reduced area. Both times are proportional to
$\beta^{-1}$, and for this reason, our numerical results are reported in
terms of the scaled time $\beta t$.
\begin{table}[htp]
  \centering
  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
  inflating ($t_\mathrm{inflate}$).}
  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
    $\beta$ & $t_\mathrm{steady}$  & ratio 
            & $t_\mathrm{inflate}$ & ratio \\
    \midrule
    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
              & $2.17 \times 10^{-2}$ & --- \\ 
    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
                $1.25 \times 10^{-1}$ & 5.76 \\
    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
                $1.59 \times 10^{0}$ & 12.72 \\
    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
                $2.19 \times 10^{1}$ & 13.77 \\
    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
                $2.14 \times 10^{2}$ & 9.77 \\
    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
                $2.20 \times 10^{3}$ & 10.14 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The steady state shape of a semi-permeable vesicle with varying
  flow rates and semi-permeability rates. The circled vesicles
  correspond to the simulations in part (a).}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
\begin{figure*}[htp]
  \ifTikz
  \centering
  \input{figures/parabolicComposite.tikz}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
  a semi-permeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The fluid flux along the red
  regions is into the vesicle, and the fluid flux along the blue regions
  is out of the vesicle.  (b) The steady state inclination angle for
  four different flow velocities. The steady state shapes are
  superimposed. (c) The reduced area of the slipper formed with the flow
  rate of 800 $\mu m/s$. (d) The vesicle shape shown with the background
  imposed flow. The channel width is 12.5 times larger than the vesicle
  radius. The corresponding reduced area of each vesicle is indicated by
  the marks in plot (c).}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry}

Velocity scale is $100\mu$m/s.

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
  the vesicle height is initially $10\mu$m, and the maximum background
  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
  into the vesicle, and the fluid flux along the blue regions is out of
  the vesicle.}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Quiescent Flow} 
\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a): Snapshots of four
  semi-permeable vesicles with $\beta = 10^{-3}$ submerged in a
  quiescent flow. The fluid flux along the red regions is into the
  vesicle, and the fluid flux along the blue regions is out of the
  vesicle. In all cases, the vesicle reaches a steady state circular
  shape. (b): The reduced area of each of the simulations. The
  particular snapshots in (a) occur at the marks along the curve.}
\end{figure*}
Our analysis shows that a semi-permeable vesicle in a quiescent flow
relaxes to a circle at a rate that is proportional to $\beta$, and the
steady state tension is $\Lambda = 2\pi^2/L^2$. Therefore, the times for
the vesicle to deviate from its initial reduced area and to reach its
steady state are proportional to $\beta^{-1}$. This is verified for a
vesicle with initial reduced area $\alpha = 0.65$ and with different
semi-permeability rates. In Table~\ref{tbl:ellipseRelaxTimes} we report
the required time, $t_\mathrm{steady}$, for the vesicle's reduced area
to be within 1.3\% of its steady state reduced area, and the required
time, $t_\mathrm{inflate}$, for the vesicle's reduced area to exceed
1.3\% of its initial reduced area. Both times are proportional to
$\beta^{-1}$, and for this reason, our numerical results are reported in
terms of the scaled time $\beta t$.
\begin{table}[htp]
  \centering
  \caption{\label{tbl:ellipseRelaxTimes} The time for a semi-permeable
  vesicle to its steady state ($t_\mathrm{steady}$) and to begin
  inflating ($t_\mathrm{inflate}$).}
  \begin{tabular}{C{0.8cm}C{2cm}C{0.8cm}C{2cm}C{0.8cm}}
    $\beta$ & $t_\mathrm{steady}$  & ratio 
            & $t_\mathrm{inflate}$ & ratio \\
    \midrule
    $10^{0}$  & $6.45 \times 10^{0}$ & ---  
              & $2.17 \times 10^{-2}$ & --- \\ 
    $10^{-1}$ & $2.00 \times 10^{1}$ & 3.10 & 
                $1.25 \times 10^{-1}$ & 5.76 \\
    $10^{-2}$ & $9.61 \times 10^{1}$ & 4.81 & 
                $1.59 \times 10^{0}$ & 12.72 \\
    $10^{-3}$ & $8.36 \times 10^{2}$ & 8.71 & 
                $2.19 \times 10^{1}$ & 13.77 \\
    $10^{-4}$ & $8.15 \times 10^{3}$ & 9.74 & 
                $2.14 \times 10^{2}$ & 9.77 \\
    $10^{-5}$ & $8.03 \times 10^{4}$ & 9.85 & 
                $2.20 \times 10^{3}$ & 10.14 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Shear Flow}
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/shearComposite.tikz}
  \else
  \includegraphics{figures/shearComposite.pdf}
  \fi
  \caption{\label{fig:shearComposite} (a) The reduced area of a
  semi-permeable vesicle with $\beta = 10^{-3}$ initialized with four
  different reduced areas in a shear flow with two different flow rates.
  (b) The steady state shape of a semi-permeable vesicle with varying
  flow rates and semi-permeability rates. The circled vesicles
  correspond to the simulations in part (a).}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
\begin{figure*}[htp]
  \ifTikz
  \centering
  \input{figures/parabolicComposite.tikz}
  \else
  \includegraphics{figures/parabolicComposite.pdf}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The steady state shape of
  a semi-permeable vesicle submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The fluid flux along the red
  regions is into the vesicle, and the fluid flux along the blue regions
  is out of the vesicle.  (b) The steady state inclination angle for
  four different flow velocities. The steady state shapes are
  superimposed. (c) The reduced area of the slipper formed with the flow
  rate of 800 $\mu m/s$. (d) The vesicle shape shown with the background
  imposed flow. The channel width is 12.5 times larger than the vesicle
  radius. The corresponding reduced area of each vesicle is indicated by
  the marks in plot (c).}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semi-Permeable Vesicle in a Contracting Geometry} 
We expose a single semi-permeable vesicle to even larger deformations by
simulating its hydrodynamics in a contracting microfluidic geometry.
Similar to~\cite{wu2015critical}, we consider a channel whose width
gradually reduces from $16\mu$m to $1.6\mu$m and then immediately opens
again to $16\mu$m (Figure~\ref{fig:contractingComposite}). We impose a
Poiseuille flow at the inlet and outlet with a constant maximum flow
rate of $U_{\max}$. We initialize a semi-permeable vesicle with $\alpha
= 0.65$ that spans $10\mu$m of the total channel width and investigate
the effects of the permeability rate and the maximum flow velocity. We
color the vesicle according to the sign of its flux---fluid flows
into the vesicle in red regions and out of the vesicle in blue
regions.

In Figures~\ref{fig:contractingComposite}(a)
and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
with different permeability rates, and
Figure~\ref{fig:contractingComposite}(c) shows that the reduced area as
a function of the vesicles' location. For sufficiently large
permeability rates, the vesicle initially inflates, but then deflates as
it passes through the constriction. However, if the semi-permeability
rate is too low, the vesicle is too large when it reaches the narrowest
part of the channel, and it is unable to pass. In
Figures~\ref{fig:contractingComposite}(d)
and~\ref{fig:constractingComposite}{e}, we plot snapshots of vesicles
with different imposed maximum velocities, and
Figure~\ref{fig:contractingComposite}(f) shows that the reduced area as
a function of the vesicles' location. At low velocities, the vesicle
inflates similar to the unbounded parabolic flow example, and it is
unable to pass through the constrictions. However, higher flow rates
result in additional deflation and the vesicle passes through the
contraction.

To understand long term effects of a vesicle passing through a
contracting geometry, in Figures~\ref{fig:contractingComposite}(g) we
simulate a vesicle passing six times through the contracting geometry.
In Figure~\ref{fig:contractingComposite}(h), we show that the vesicle
deflates each time it passes through the constriction followed by a
rapid inflation. The total area loss over the history of the vesicle is
almost 50\%. In Figure~\ref{fig:contractingComposite}(i), we show the
vesicle velocity as a function of the vesicle's center of mass. As the
vesicle passes through the contraction, it accelerates followed by a
rapid deacceleration once it has passed through the contraction.

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} (a) A semi-permeable vesicle
  passing through a contracting geometry similar to the experimental
  device in~\cite{}. The narrowest part of the channel is $1.6\mu$m, 
  the vesicle height is initially $10\mu$m, and the maximum background
  flow velocity is $316\mu$m/s. The fluid flux along the red regions is
  into the vesicle, and the fluid flux along the blue regions is out of
  the vesicle.}
\end{figure*}
